Setting parameters for biological~models with ANIMO

### 2014-04-04 Presentazione/Presentazione_SynCoP.tex
Some other images were forgotten
Adding the graph comparison and other parameter-related part

@@

% A che domande biologiche rispondiamo con ANIMO
% Approccio: interaction-based, discrete levels, sottolinea la concorrenza
% Magari evitare di mostrare modelli TA
% Come funziona la modellazione in ANIMO: topologia, scenari, parametri (con esempi) (tipo Gene?)
% Come funziona l'esperimento in silico (simulazione, model checking, grafici sim+data, slider)
% Demo breve
% Piani futuri: generazione di ipotesi, model checking (esempi??), high-performance analysis
\listfiles

@@

  \frame{ \frametitle{Signalling Pathways}
    \begin{center}
      %\pgfuseimage{pathway-semplificato}
      \begin{minipage}[c]{.9\textwidth}%
	\pgfuseimage{signaling-schematic}\\[-1ex]%
	{\tiny Credit: National Science Foundation}%
      \end{minipage}
    \end{center}
% Cells receive external signals (depicted in yellow) through sensing molecules--or receptors--(depicted in aqua) embedded in the cell membrane. This information is transmitted sequentially throughout the cell via signaling networks. Arrows indicate the direction of information flow between signaling molecules A, B, C, and D in this illustration. Bayesian network modeling can determine that molecules A and B are in the same pathway. It can also tell if the activity of molecule B relies on a signal from molecule A. In many cases, communication from outside the cell follows signaling pathways to the nucleus, where the information activates genes that control the cell's response.
  }

@@

\frame{\frametitle{All good and nice, but\dots}
{\Huge How to find the parameters?}\\ \ \\
\begin{itemize}
  \item<2-> ANIMO models are centered around the topology more than the parameters
  \item<3-> ANIMO requires less parameters than ODEs
  \item<4-> 
\end{itemize}
but we still need to estimate them
}

>>>>

\newcommand*{\xdash}[1][3em]{\rule[0.5ex]{#1}{0.55pt}}

@@

% A che domande biologiche rispondiamo con ANIMO
% Approccio: interaction-based, discrete levels, sottolinea la concorrenza
% Magari evitare di mostrare modelli TA
% Come funziona la modellazione in ANIMO: topologia, scenari, parametri (con esempi) (tipo Gene?)
% Come funziona l'esperimento in silico (simulazione, model checking, grafici sim+data, slider)
% Demo breve
% Piani futuri: generazione di ipotesi, model checking (esempi??), high-performance analysis
%\listfiles

@@

\frame{ \frametitle{Signalling Pathways}
  \begin{center}
    %\pgfuseimage{pathway-semplificato}
    \begin{minipage}[c]{.9\textwidth}%
      \pgfuseimage{signaling-schematic}\\[-1ex]%
      {\tiny Credit: National Science Foundation}%
    \end{minipage}
  \end{center}
}

@@

\def\graphA{\includegraphics[scale=0.13]{images/feedback_params_graphA}}
\newlength\graphASize
\setlength\graphASize{\heightof{\graphA}}

\frame{\frametitle{All good and nice, but\dots}
{\Huge How to find the parameters?}\\
\begin{itemize}
  \item<1-> Insert parameters manually\only<1-1>{\\\includegraphics[scale=0.3]{images/scenario_parameter_dialog}}
  \item<2-> Compare model versions \emph{subtracting} their activity graphs\only<2-2>{\\\begin{center}\begin{minipage}[c][\graphASize]{\textwidth}\begin{center}\graphA {\Huge -} \includegraphics[scale=0.13]{images/feedback_params_graphD}\end{center}\end{minipage}\xdash[12em]\\ \includegraphics[scale=0.1]{images/difference_network_d-a_larger}\end{center}}
\end{itemize}

}
